Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-29 paper/paper.tex
altered bound on plot-ave and edited text in paper Tested everything on quipu.

\section{Stability Analysis}
We have found that in both methods of simulation there is a lower
length scale that characterizes much of the behavoir.  Regular
oscillatory behavoir between two poles at opposite ends of the longer
cellular direction is found in cells which are long enough in one
dimension for the reaction chain to be unstable but short enough in
the perpendicular dimension to be stable.  The limits are seen when
both dimensions are too short to be unstable, so that initial
assymetry in protein concentration relaxes into a state of no
oscillation.  In these cell sizes, the deterministic simulations show
a motionless steady state and the stochastic simulations show random
fluctuations without any bulk behavoir (see Figure~\ref{box-mannik}).

@@

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
\fixme{should I say anything about different/large sizes?}
We have made and studied plots and movies of the MinD in a number of
simulated cell shapes and sizes. We have found that the deterministic
simulations of the protein reaction sequence discussed above results
in robust oscillatory behavoir of polar selection and oscillation in
not only symmetrical shapes, such as the wild type pill shape, but
also in very assymetrical, flatttened cells, such as those studied by
Mannik.  This differs with Mannik's experimental findings that show
much less regular behavoir, with a large variation in the location of
maxima.  On the other hand, our stochastic simulations show both
robust pole to pole oscillations in the symmetric cells and irregular
behavoir in the assymetrical shapes, agreeing well with Mannik's
experimental findings.

>>>>

\section{Stability Analysis}
\label{sec:stability-analysis}
We have found that in both methods of simulation there is a lower
length scale that characterizes much of the behavoir.  Regular
oscillatory behavoir between two poles at opposite ends of the longer
cellular direction is found in cells which are long enough in one
dimension for the reaction chain to be unstable but short enough in
the perpendicular dimension to be stable.  The limits are seen when
both dimensions are too short to be unstable, so that initial
assymetry in protein concentration relaxes into a state of no
oscillation.  In these cell sizes, the deterministic simulations show
a motionless steady state and the stochastic simulations show random
fluctuations without any bulk behavoir (see Figure~\ref{box-mannik}).

@@

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
\fixme{should I say anything about different/large sizes?}  We have
made movies out of color plots of MinD concentration, integrated along
the flattened axis, in which each frame is seperated in simulation
time by a half second. Our simulations include the two flattened cell
shapes that are reported in Manniks paper, a few other 'irregular'
shapes of our own creation, triangle shaped flattened cells, and a
symetric 'stadium' shaped cell. For each of these shapes we have
varied the size, from roughly twice the dimensions of Mannik's
reported cells down to the smaller sizes refered to in
section~\ref{sec:stability-analysis}.

We have found that the deterministic simulations of the protein
reaction sequence discussed above results in robust oscillatory
behavoir of polar selection and oscillation in not only symmetrical
shapes, such as the wild type pill shape, but also in very
assymetrical, flatttened cells, such as those studied by Mannik.  This
differs with Mannik's experimental findings that show much less
regular behavoir, with a large variation in the location of maxima.
On the other hand, our stochastic simulations show both robust pole to
pole oscillations in the symmetric cells and irregular behavoir in the
assymetrical shapes, agreeing well with Mannik's experimental
findings.
